UKB Models

### 2023-10-05 ukb_mods.Rmd
more robust parsing of sigma moments

```{r}
lh_SA_middletemporal_mod <- readRDS("ukb/gamlss_objs/lh_SA_middletemporal_mod.rds")
summary(lh_SA_middletemporal_mod)

formula(lh_SA_middletemporal_mod, what="sigma")
coef(lh_SA_middletemporal_mod, what="sigma") %>%
  names()

sfit <- summary(lh_SA_middletemporal_mod)

sfit$coef.table

#to get a list of all the slots in the object
str(sfit)
```

>>>>

```{r}
lh_SA_middletemporal_mod <- readRDS("ukb/gamlss_objs/lh_SA_middletemporal_mod.rds")
a <- summary(lh_SA_middletemporal_mod)
dim(a)

#sigma coefficients
coef(lh_SA_middletemporal_mod, what="sigma") %>%
  names()

test <- confint(lh_SA_middletemporal_mod)
colnames(test)
rownames(test)
test["sigma.sexMale", "97.5 %"]
df.test <- as.data.frame(test)
df.test$params <- rownames(df.test)
# Remove the row names from the dataframe
rownames(df.test) <- NULL

df.test
#using drop1 to get significance, gamlss book p 125 for df info
#get df from OG model - not sure how this would be affected by using stepGAIC?

str(lh_SA_middletemporal_mod)
lh_SA_middletemporal_mod$sigma.nl.df

#start df with confidence intervals
confint.matrix <- confint(lh_SA_middletemporal_mod)
df <- as.data.frame(confint.matrix) %>%
  rownames_to_column(var = "moment.param") %>%
  mutate(
    moment = sapply(strsplit(moment.param, "\\."), `[`, 1),
    param = sub("^[^.]+\\.", "", moment.param)
  )

#now that we have the moments, add the rest of the summary info
sum.table <- summary(lh_SA_middletemporal_mod)
df2 <- as.data.frame(sum.table) %>%
  rownames_to_column(var = "param")
#check
rownames(sum.table) == df$param

find.param <- function(gamlss.rds.file, moment, string) {
  #USE WITH sapply(USE.NAMES=TRUE) to keep file names with values!
  gamlss.obj <- readRDS(gamlss.rds.file)
  sigma.coeff.list <- coef(gamlss.rds.file, what= moment) %>%
    names()
  any(sapply(sigma.coeff.list, function(x) grepl(string, x, ignore.case = TRUE)))
}
find.param(lh_SA_middletemporal_mod, "sigma", "sex")

readRDS("ukb/gamlss_objs/rh_Vol_parsopercularis_mod.rds")

```
